---
title: "function-01-documentation"
output: html_document
date: "2023-10-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load-packages, include=FALSE}
library(dplyr)
library(magrittr)
library(knitr)
library(ggplot2)
```

## Function
```{r echo_example, echo=TRUE}
function1 <- function(data, order_by){
  
  # A transformation function that perform some reordering on the dataset in argument
  # 
  # argument: 
  #   data (a dateset). Here we use mpg dataset.
  #   order_by: specifiying a numeric column to reorder the dataset. only 'displ', 
  #             'year', 'cyl', 'cty', 'hwy' are ligal input arguments. 
  # 
  # return: tibble after transformation
  
  tb <- data %>% arrange(order_by)
  
  return (tb)
}
```
## Parameters
#### 1. parameter: data
The first input parameter of the function is a dataset. Here the 'mpg' dataset in package 'ggplot2' is selected as my input dataset.

#### 2. parameter 2: order_by
Specifiy a numeric column to reorder the dataset. only 'displ', 'year', 'cyl', 'cty', 'hwy' are ligal input parameters.

For example, we use mpg data and order by displ, the following table would be the output. The output tibble is ordered by "displ"
```{r}
function1(mpg, mpg$displ)
```
## Appendix: all code in this documentation

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE} 
# this chunk generates the complete code appendix. 
# eval=FALSE tells R not to run (``evaluate'') the code here (it was already run before).
```
